Estimating the dynamics of SPARQL query results using binary classification

### 2019-08-06 main.tex
hyperref fixes

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks, 
    linkcolor={black},
    citecolor={black}, urlcolor={black},
    pdftitle={Estimating the dynamics of SPARQL query results},    % title
    pdfauthor={Alberto Moya, Aidan Hogan},     % author
    pdfsubject={ISWC 2019},   % subject of the document
    pdfkeywords={SPARQL;} {Linked Data;} {Dynamics;} {Wikidata;}, % list of keywords
}

>>>>

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks, 
    linkcolor={black},
    citecolor={black}, urlcolor={black},
    pdftitle={Estimating the dynamics of SPARQL query results using binary classification},    % title
    pdfauthor={Alberto Moya, Aidan Hogan},     % author
    pdfsubject={QuWeDa @ ISWC 2019},   % subject of the document
    pdfkeywords={SPARQL;} {Linked Data;} {Dynamics;} {Wikidata;}, % list of keywords
}
